Legends for supplementary material

### 2019-04-04 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends
updated legend

**Supplementary Table 5. Data Summaries and Imbalance Ratios.** The total number of genomic bins included in the complete, training, and testing sets, as well as the subsequent imbalance ratios across resolutions and cell lines. Imbalance ratio is defined as the ratio of genomic bins that overlapped a flanked TAD boundary (minority class), divided by the number of genomic bins that did not overlap a flanked TAD boundary (majority class).

@@

**Supplementary Figure 14. Variable importance of the top 20 most predictive genomic annotations for models using no resampling technique with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model with distance-type predictors at the 10 kb data resolution, while not performing a class balancing technique, for each cell line respectively.

**Supplementary Figure 15. Variable importance of the top 20 most predictive genomic annotations for models using random over-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random over-sampling to create balanced classes, for each cell line respectively.

**Supplementary Figure 16. Variable importance of the top 20 most predictive genomic annotations for models using random under-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random under-sampling to create balanced classes, for each cell line respectively.

>>>>

<!--
**Supplementary Table 5. Data Summaries and Imbalance Ratios.** The total number of genomic bins included in the complete, training, and testing sets, as well as the subsequent imbalance ratios across resolutions and cell lines. Imbalance ratio is defined as the ratio of genomic bins that overlapped a flanked TAD boundary (minority class), divided by the number of genomic bins that did not overlap a flanked TAD boundary (majority class).
-->

**Supplementary Figure 15. Data summaries in the form of barplots for the GM12878 (red) and K562 (blue) cell lines.** (A) The total number of genomic bins created by partitioning the linear genome into unit intervals corresponding to the resolution of the relevant domain data. (B) Subsequent imbalance ratios, defined as the ratio of the number of bins that overlapped with a flanked TAD boundary to the number of bins that did not overlap with a flanked TAD boundary.

@@

**Supplementary Figure 14A. Variable importance of the top 20 most predictive genomic annotations for models using no resampling technique with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model with distance-type predictors at the 10 kb data resolution, while not performing a class balancing technique, for each cell line respectively.

**Supplementary Figure 14B. Variable importance of the top 20 most predictive genomic annotations for models using random over-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random over-sampling to create balanced classes, for each cell line respectively.

**Supplementary Figure 14C. Variable importance of the top 20 most predictive genomic annotations for models using random under-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random under-sampling to create balanced classes, for each cell line respectively.
